The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-17 manuscript/manuscript.Rnw
discuss CD9 in the core placenta

The high expression of components of the EGFR signaling pathway in the
core placenta transcriptome (including \textit{GRB2}, \textit{RALB})
as well as annexins which are involved in the location of EGF receptor
localization (\textit{ANXA1} and \textit{ANXA2}) in the core placenta
is consistent with previous findingsshowing that alterations to the
EGF signaling system change invasion of trophoblast cells into the
spiral arteries~\cite{Armant.ea2015:Reducedexpressionofepidermal}.

>>>>

The high expression of components of the EGFR signaling pathway in the
core placenta transcriptome (including \textit{GRB2}, \textit{RALB})
as well as annexins which are involved in the location of EGF receptor
localization (\textit{ANXA1} and \textit{ANXA2}) in the core placenta
is consistent with previous findingsshowing that alterations to the
EGF signaling system change invasion of trophoblast cells into the
spiral arteries~\cite{Armant.ea2015:Reducedexpressionofepidermal}.
Another component of the core placenta transcriptome, \textit{CD9},
has been shown to suppress \human extravillous trophoblast
invasion~\cite{Matsumoto.ea2016:CD9suppresseshumanextravillous}, and
we hypothesize that it is responsible for maintaining the balance
between invasion and attachment in the other placentas examined here
as well.
